---
title: "Sample Template for my slides"
author: "Dr. Mine Dogucu"
output: 
  xaringan::moon_reader:
    css: slide-style.css
    seal: false
    nature:
      ratio: 16:9
      highlightStyle: "pygments"
      highlightLines: true
      highlightLanguage: "r"


---

class: title-slide

```{r echo = FALSE}
library(fabricerin)
```

<br>
<br>
.right-panel[ 

# `r rmarkdown::metadata$title`
## `r rmarkdown::metadata$author`
]

---

class: inverse middle center


.font150[Some new topic]



---



```{r echo = FALSE}
fabric_drawing(cid = "canvas1", 
               cwidth = 1100, 
               cheight = 550, 
               cfill = "#e2d7c4", 
               drawingWidth = 2, 
               gumSize = 32)


```

---


.left-panel[
```{r}
library(magrittr)
lm(mpg ~ am, data = mtcars) %>% 
  broom::tidy()
```


]

.right-panel[

```{r echo = FALSE}
fabric_drawing(cid = "canvas2", 
               cwidth = 650, 
               cheight = 550, 
               cfill = "#e2d7c4", 
               drawingWidth = 2, 
               gumSize = 32)


```
]
---

## Notes

>Some brilliant quote by someone  

.important[
Note that your professor is here to support you and you will do great things in this course.
]


- Great thing 1

- Great thing 2

Course website is [introdata.science](introdata.science)

.smallish[

Some footnote

]

---

## R code

```{r, message=FALSE, eval = FALSE}
library(beep)
beepr()
```

Also mention it in line `beepr::beep()`


Or even highlight it

```{r, message=FALSE, eval = FALSE}
library(beep)
beepr() #<<
```
---

## Math

$$x+7\beta$$





