---
title: "More ggplot"
author: "Dr. Mine Dogucu"
output: 
  xaringan::moon_reader:
    css: ["slide-style.css"]
    seal: false
    nature:
      ratio: 16:9
      highlightStyle: "pygments"
      highlightLines: true
      highlightLanguage: "r"
---

class: title-slide


<br>
<br>
.right-panel[ 

# `r rmarkdown::metadata$title`
## `r rmarkdown::metadata$author`
]




```{r echo = FALSE, message=FALSE}
xaringanExtra::use_panelset()
library(palmerpenguins)
library(tidyverse)
library(titanic)
library(janitor)
library(scales)
library(fivethirtyeight)
titanic <- titanic_train %>% 
  clean_names() %>% 
  select(survived, pclass, sex, age, fare, embarked) %>% 
  mutate(pclass = case_when(pclass == 1 ~ "First", 
                            pclass == 2 ~ "Second",
                            pclass == 3 ~ "Third"),
         embarked = case_when(embarked == "S" ~ "Southampton",
                              embarked == "C" ~ "Cherbourg",
                              embarked == "Q" ~ "Queenstown"),
         embarked = as.factor(embarked),
         sex = as.factor("sex"),
         survived = as.logical(survived))
```




---

class: middle 
 

.panelset[
.panel[

.panel-name[Plot]

```{r echo = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) 
```

]

.panel[

.panel-name[English]
- Using the `penguins` data,   
- Map `bill depth` to x-axis, `bill length` to y-axis, `species` to shape and color.
- Add a layer of points and set the size of the points to 4.
]

.panel[
.panel-name[R]
```{r eval = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) 
```

]

]


---
class: middle 

## Labs


.panelset[
.panel[

.panel-name[Plot]

```{r echo = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  labs(x = "Bill Depth (mm)", #<<
       y = "Bill Length (mm)", #<<
       title = "Palmer Penguins") #<<
```

]

.panel[

.panel-name[English]
- Using the `penguins` data,   
- Map `bill depth` to x-axis, `bill length` to y-axis, `species` to shape.
- Add a layer of points and set the size of the points to 4.
- .highlight-text[Add labels to x-axis (Bill Depth(mm)), y-axis (Bill Length(mm)), and the title of the plot (Palmer Penguins).]



.panel[
.panel-name[R]
```{r eval = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  labs(x = "Bill Depth (mm)", #<<
       y = "Bill Length (mm)", #<<
       title = "Palmer Penguins") #<<
```

]

]



]

---

.left-panel[
```{r eval = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point() +
  labs(x = "Bill Depth (mm)", 
       y = "Bill Length (mm)", 
       title = "Palmer Penguins") +
  theme_bw() #<<
  
```

]

.right-panel[
```{r echo = FALSE, fig.height=5, warning = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point() +
  labs(x = "Bill Depth (mm)",
       y = "Bill Length (mm)",
       title = "Palmer Penguins") +
  theme_bw()
```

]

---

class: middle

## Themes

.panelset[


.panel[

.panel-name[`theme_gray()`]

```{r echo = FALSE, fig.height=4, fig.align='center', warning = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point() +
  labs(x = "Bill Depth (mm)",
       y = "Bill Length (mm)",
       title = "Palmer Penguins") +
  theme_gray()
```

]

.panel[

.panel-name[`theme_bw()`]

```{r echo = FALSE, fig.height=4, fig.align='center', warning = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point() +
  labs(x = "Bill Depth (mm)",
       y = "Bill Length (mm)",
       title = "Palmer Penguins") +
  theme_bw()
```

]

.panel[

.panel-name[`theme_classic()`]

```{r echo = FALSE, fig.height=4, fig.align='center', warning = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point() +
  labs(x = "Bill Depth (mm)",
       y = "Bill Length (mm)",
       title = "Palmer Penguins") +
  theme_classic()
```

]

.panel[

.panel-name[`theme_dark()`]

```{r echo = FALSE, fig.height=4, fig.align='center', warning = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point() +
  labs(x = "Bill Depth (mm)",
       y = "Bill Length (mm)",
       title = "Palmer Penguins") +
  theme_dark()
```

]

.panel[
.panel-name[`theme_minimal()`]

```{r echo = FALSE, fig.height=4, fig.align='center', warning = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point() +
  labs(x = "Bill Depth (mm)",
       y = "Bill Length (mm)",
       title = "Palmer Penguins") +
  theme_minimal()
```

]


.panel[
.panel-name[`theme_void()`]

```{r echo = FALSE, fig.height=4, fig.align='center', warning = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point() +
  labs(x = "Bill Depth (mm)",
       y = "Bill Length (mm)",
       title = "Palmer Penguins") +
  theme_void()
```

]
]

---

.left-panel[

```{r eval = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point() +
  labs(x = "Bill Depth (mm)", 
       y = "Bill Length (mm)", 
       title = "Palmer Penguins") +
  theme_bw() +
  theme(text = element_text(size=20)) #<<
  
```

]

.right-panel[

```{r echo = FALSE, fig.height=5, warning = FALSE}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point() +
  labs(x = "Bill Depth (mm)",
       y = "Bill Length (mm)",
       title = "Palmer Penguins") +
  theme_bw() +
  theme(text = element_text(size=20))
```
]


---

```{r eval = FALSE}
?theme
```


---

class: middle 
 

.left-panel[

```{r eval = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  facet_grid(.~species) #<<
```

]

.right-panel[
```{r echo = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  facet_grid(.~species)
```
]

---

class: middle 
 

.left-panel[

```{r eval = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  facet_grid(species~.) #<<
```

]

.right-panel[
```{r echo = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  facet_grid(species~.)
```
]

---

class: middle 
 

`library(scales)`

.left-panel[

```{r eval = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  scale_x_continuous(breaks = breaks_width(2)) 
```

]

.right-panel[
```{r echo = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  scale_x_continuous(breaks = breaks_width(2)) 
  
```
]

---

class: middle 
 

`library(scales)`

.left-panel[

```{r eval = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  scale_x_continuous(breaks = c(18.5, 20)) 
```

]

.right-panel[
```{r echo = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  scale_x_continuous(breaks = c(18.5, 20)) 
  
```
]

---


class: middle 
 

`library(scales)`

.left-panel[

```{r eval = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  scale_x_continuous(breaks = c(18.5, 20)) +
  scale_color_manual(values = c("firebrick",
                                "deepskyblue4",
                                "goldenrod"))
```

]

.right-panel[
```{r echo = FALSE, fig.align='center', warning = FALSE, fig.height=5}
ggplot(penguins,
       aes(x = bill_depth_mm,
           y = bill_length_mm,
           shape = species,
           color = species)) +
  geom_point(size = 4) +
  scale_color_manual(values = c("firebrick",
                                "deepskyblue4",
                                "goldenrod"))
  
```
]



--

Check out [the ggplot flipbook](https://evamaerey.github.io/ggplot_flipbook/ggplot_flipbook_xaringan.html#1) for some inspiration. 

