---
title: "API wrappers"
author: "Dr. Mine Dogucu"
output: 
  xaringan::moon_reader:
    css: slide-style.css
    seal: false
    nature:
      ratio: 16:9
      highlightStyle: "pygments"
      highlightLines: true
      highlightLanguage: "r"
---

class: title-slide


<br>
<br>
.pull-right[ 

# `r rmarkdown::metadata$title`
## `r rmarkdown::metadata$author`
]

---

```{r echo = FALSE, message = FALSE}
library(tidyverse)
```


## Two ways of web scraping

**Screen scraping**: What we have done by extracting the data from the source code of the website. 

--

**Web APIs** (Application Programming Interface): Website offers a set of http requests that you can use use to access data. 

--

However, there are wrapper packages for some APIs. In short, you can connect to certain APIs (i.e. if the package exists) without having to know about too much about working with APIs.

---

## Example

```{r}
library(spotifyr)
```


---

**Get Access to the Spotify API**

https://developer.spotify.com/dashboard/login

You will get a Client ID and Client Secret

---

## Authentication 

Do not use this specific method on a public computer.

--

```{r eval = FALSE}
usethis::edit_r_environ()
```

--

In your .Renviron write the following and save your file. The `XXXXXXXXX` comes from your own Spotify developer account.

```{r eval = FALSE}
SPOTIFY_CLIENT_ID = XXXXXXXXXXXXXXXXXXXXXXXXXXX
SPOTIFY_CLIENT_SECRET = XXXXXXXXXXXXXXXXXXXXXXXX
```

---

class: middle center

[List of functions in `spotifyr` package](https://www.rcharlie.com/spotifyr/reference/index.html)

---

[https://open.spotify.com/artist/6vWDO969PvNqNYHIOW5v0m](https://open.spotify.com/artist/6vWDO969PvNqNYHIOW5v0m) 

--

```{r}
get_artist("6vWDO969PvNqNYHIOW5v0m")
```

---

```{r}
get_artist("6vWDO969PvNqNYHIOW5v0m") %>% 
  str()
```
