---
title: "Changing Variables"
author: "Dr. Mine Dogucu"
output: 
  xaringan::moon_reader:
    css: ["slide-style.css"]
    seal: false
    nature:
      ratio: 16:9
      highlightStyle: "pygments"
      highlightLines: true
      highlightLanguage: "r"
---

class: title-slide

```{r child = "../setup.Rmd"}
```


```{r echo = FALSE, message = FALSE}
library(tidyverse)
options(scipen = 999)
```


<br>
<br>
.right-panel[ 

# `r rmarkdown::metadata$title`
## `r rmarkdown::metadata$author`
]

---

```{r echo = FALSE, message = FALSE}
lapd <- read_csv(here::here("slides/data/Police_Payroll.csv")) %>% 
  janitor::clean_names() %>% 
  filter(year == 2018) %>% 
  select(job_class_title, 
         employment_type, 
         base_pay)
```



```{r}
glimpse(lapd)
```

**Goal**: 

Create a new variable called `base_pay_k` that represents `base_pay` in thousand dollars.

---

```{r}
lapd %>% 
  mutate(base_pay_k = base_pay/1000)
```


---

```{r}
glimpse(lapd)
```

**Goal**: 

Create a new variable called `base_pay_level` which has `Less Than Median`, `Greater Than Median`. We will consider $62474 as the median (from previous lecture).

---


Let's first check to see there is anyone earning exactly the median value.

```{r}
lapd %>% 
  filter(base_pay == 62474)
```


---

```{r}
lapd %>% 
  mutate(base_pay_level = if_else(base_pay < 62474, 
                                  "Less Than Median", 
                                  "Greater Than Median"))
```


---


```{r}
glimpse(lapd)
```

**Goal**: 

Create a new variable called `base_pay_level` which has `Less Than 0`, `No Income`, `Less than Median and Greater than 0` and `Greater than Median`. We will consider $62474 as the median (from previous lecture).



---

```{r}
lapd %>% 
  mutate(base_pay_level = case_when(
    base_pay < 0 ~ "Less than 0", 
    base_pay == 0 ~ "No Income",
    base_pay < 62474 & base_pay > 0 ~ "Less than Median, Greater than 0",
    base_pay > 62474 ~ "Greater than Median")) 
```

---

To see what we have created 

```{r}
lapd %>% 
  mutate(base_pay_level = case_when(
    base_pay < 0 ~ "Less than 0", 
    base_pay == 0 ~ "No Income",
    base_pay < 62474 & base_pay > 0 ~ "Less than Median, Greater than 0",
    base_pay > 62474 ~ "Greater than Median")) %>% 
  select(base_pay_level)
```


---

We can use pipes with ggplot too!

.left-panel[
```{r eval = FALSE}
lapd %>% 
  mutate(base_pay_level = case_when(
    base_pay < 0 ~ "Less than 0", 
    base_pay == 0 ~ "No Income",
    base_pay < 62474 & base_pay > 0 ~ "Less than Median, Greater than 0",
    base_pay > 62474 ~ "Greater than Median")) %>% 
  select(base_pay_level) %>% 
  ggplot(aes(x = base_pay_level)) +
  geom_bar()
```
]

.right-panel[
```{r echo = FALSE}
lapd %>% 
  mutate(base_pay_level = case_when(
    base_pay < 0 ~ "Less than 0", 
    base_pay == 0 ~ "No Income",
    base_pay < 62474 & base_pay > 0 ~ "Less than Median, Greater than 0",
    base_pay > 62474 ~ "Greater than Median")) %>% 
  select(base_pay_level) %>% 
  ggplot(aes(x = base_pay_level)) +
  geom_bar()
```
]

---

```{r}
glimpse(lapd)
```

**Goal**: 

Make `job_class_title` and `employment_type` factor variables. 


---

```{r}
lapd %>% 
  mutate(employment_type = as.factor(employment_type),
         job_class_title = as.factor(job_class_title)) 
```

---

`as.factor()` - makes a vector factor  
`as.numeric()` - makes a vector numeric  
`as.integer()` - makes a vector integer  
`as.double()` - makes a vector double  
`as.character()` - makes a vector character  

---

class: middle

Once again we did not "save"
anything into `lapd`. As we work on data cleaning it makes sense not to "save" the data frames. Once we see the final data frame we want then we can "save" (i.e. overwrite) it.

---

```{r}
lapd <- 
  lapd %>% 
    mutate(employment_type = as.factor(employment_type),
           job_class_title = as.factor(job_class_title),
           base_pay_level = case_when(
             base_pay < 0 ~ "Less than 0", 
             base_pay == 0 ~ "No Income",
             base_pay < 62474 & base_pay > 0 ~ "Less than Median, Greater than 0",
             base_pay > 62474 ~ "Greater than Median")) 
```

