---
title: "Data Joins"
author: "Dr. Mine Dogucu"
output: 
  xaringan::moon_reader:
    css: ["slide-style.css"]
    seal: false
    nature:
      ratio: 16:9
      highlightStyle: "pygments"
      highlightLines: true
      highlightLanguage: "r"
---

class: title-slide

```{r child = "../setup.Rmd"}
```


```{r echo = FALSE, message = FALSE}
library(tidyverse)
options(scipen = 999)
xaringanExtra::use_panelset()

artists <- readxl::read_xlsx("../data/spotify.xlsx", sheet = "artist")
songs <- readxl::read_xlsx("../data/spotify.xlsx", sheet = "top_song")
albums <- readxl::read_xlsx("../data/spotify.xlsx", sheet = "album") %>% 
  mutate(album_release_date = lubridate::ymd(album_release_date))
```


<br>
<br>
.right-panel[ 

# `r rmarkdown::metadata$title`
## `r rmarkdown::metadata$author`
]


---

.panelset[
.panel[
.panel-name[artists]

```{r}
artists
```


]

.panel[
.panel-name[songs]

```{r}
songs
```


]

.panel[
.panel-name[albums]

```{r}
albums
```

]
]

---

## Join Functions

`something_join(x, y)` All the join functions in dplyr package are in this fashion where x represents the first data frame and y represents the second data frame.


---

.panelset[
.panel[

.panel-name[x]

```{r}
songs
```


]

.panel[

.panel-name[y]

```{r}
albums
```


]

.panel[

.panel-name[right_join()]

```{r}
right_join(songs, albums, by = "album_name")
```

]

]

`right_join()` includes all rows from `y`
---

.panelset[
.panel[

.panel-name[x]

```{r}
songs
```


]

.panel[

.panel-name[y]

```{r}
albums
```


]

.panel[

.panel-name[left_join()]

```{r}
left_join(songs, albums, by = "album_name")
```

]

]

`left_join()` includes all rows from x


---

.panelset[
.panel[

.panel-name[x]

```{r}
songs
```


]

.panel[

.panel-name[y]

```{r}
albums
```


]

.panel[

.panel-name[inner_join()]

```{r}
inner_join(songs, albums, by = "album_name")
```

]

]

`inner_join()` includes all rows that are in x **and** y

---

.panelset[
.panel[

.panel-name[x]

```{r}
songs
```


]

.panel[

.panel-name[y]

```{r}
albums
```


]

.panel[

.panel-name[full_join()]

```{r}
full_join(songs, albums, by = "album_name")
```

]

]

`full_join()` includes all rows that are in x **or** y

---


.panelset[
.panel[
.panel-name[artists]

```{r}
artists
```


]

.panel[
.panel-name[songs]

```{r}
songs
```


]

.panel[
.panel-name[albums]

```{r}
albums
```

]

.panel[
.panel-name[combined]

```{r}
full_join(artists, songs, by = "name") %>% 
  full_join(albums, by = "album_name")
  
```


]


]
